---
title: "Codebook.rmd"
author: "Dario Oviedo Rueda"
date: "September 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Information

This information came from:
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones


## Data Set Information
The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. 

The sensor signals (accelerometer and gyroscope) were pre-processed by applying noise filters and then sampled in fixed-width sliding windows of 2.56 sec and 50% overlap (128 readings/window). The sensor acceleration signal, which has gravitational and body motion components, was separated using a Butterworth low-pass filter into body acceleration and gravity. The gravitational force is assumed to have only low frequency components, therefore a filter with 0.3 Hz cutoff frequency was used. From each window, a vector of features was obtained by calculating variables from the time and frequency domain.

Check the README.txt file for further details about this dataset. 

A video of the experiment including an example of the 6 recorded activities with one of the participants can be seen in the following link: [Web Link]

An updated version of this dataset can be found at [Web Link]. It includes labels of postural transitions between activities and also the full raw inertial signals instead of the ones pre-processed into windows.




## Library and Variables used in Run_analisys.r
library('RCurl')

wd <- getwd()

udir <- 'UCI HAR Dataset'

fs <- 'UCI-HAR.zip'




## Important information
These are the steps to understand how Run_analisys.R works:
1.- The script will try to open the directory UCI HAR Dataset.
    If the directory doesn't exist, it will create it and will
    download the requeried files.
2.- The script will generate two files, Mean.csv and 
    tidyData.csv




## Mean.csv Table
This is the table that you can find in Mean.csv.
```{r}
knitr::kable(read.csv('Mean.csv', header = TRUE))
```



## TidyData.csv

These are the column names used in tidyData.csv

```{r echo=FALSE}
knitr::kable(colnames(nombres <- read.csv('UCI HAR Dataset/tidyData.csv', header = TRUE)))
```
X
Subjet
activity
tBodyAcc.mean...Y
tBodyAcc.mean...Z
tBodyAcc.std...X
tBodyAcc.std...Y
tBodyAcc.std...Z
tGravityAcc.mean...X
tGravityAcc.mean...Y
tGravityAcc.mean...Z
tGravityAcc.std...X
tGravityAcc.std...Y
tGravityAcc.std...Z
tBodyAccJerk.mean...X
tBodyAccJerk.mean...Y
tBodyAccJerk.mean...Z
tBodyAccJerk.std...X
tBodyAccJerk.std...Y
tBodyAccJerk.std...Z
tBodyGyro.mean...X
tBodyGyro.mean...Y
tBodyGyro.mean...Z
tBodyGyro.std...X
tBodyGyro.std...Y
tBodyGyro.std...Z
tBodyGyroJerk.mean...X
tBodyGyroJerk.mean...Y
tBodyGyroJerk.mean...Z
tBodyGyroJerk.std...X
tBodyGyroJerk.std...Y
tBodyGyroJerk.std...Z
tBodyAccMag.mean..
tBodyAccMag.std..
tGravityAccMag.mean..
tGravityAccMag.std..
tBodyAccJerkMag.mean..
tBodyAccJerkMag.std..
tBodyGyroMag.mean..
tBodyGyroMag.std..
tBodyGyroJerkMag.mean..
tBodyGyroJerkMag.std..
fBodyAcc.mean...X
fBodyAcc.mean...Y
fBodyAcc.mean...Z
fBodyAcc.std...X
fBodyAcc.std...Y
fBodyAcc.std...Z
fBodyAcc.meanFreq...X
fBodyAcc.meanFreq...Y
fBodyAcc.meanFreq...Z
fBodyAccJerk.mean...X
fBodyAccJerk.mean...Y
fBodyAccJerk.mean...Z
fBodyAccJerk.std...X
fBodyAccJerk.std...Y
fBodyAccJerk.std...Z
fBodyAccJerk.meanFreq...X
fBodyAccJerk.meanFreq...Y
fBodyAccJerk.meanFreq...Z
fBodyGyro.mean...X
fBodyGyro.mean...Y
fBodyGyro.mean...Z
fBodyGyro.std...X
fBodyGyro.std...Y
fBodyGyro.std...Z
fBodyGyro.meanFreq...X
fBodyGyro.meanFreq...Y
fBodyGyro.meanFreq...Z
fBodyAccMag.mean..
fBodyAccMag.std..
fBodyAccMag.meanFreq..
fBodyBodyAccJerkMag.mean..
fBodyBodyAccJerkMag.std..
fBodyBodyAccJerkMag.meanFreq..
fBodyBodyGyroMag.mean..
fBodyBodyGyroMag.std..
fBodyBodyGyroMag.meanFreq..
fBodyBodyGyroJerkMag.mean..
fBodyBodyGyroJerkMag.std..
fBodyBodyGyroJerkMag.meanFreq..



I left the comands used to get the variable names for Markdown in case that somebody need it.
